---
title: "Stoppage time models for the 2020 season"
output: pdf_document
---

```{r, warning = FALSE, message = FALSE}
library(dplyr)
library(ggplot2)
library(CVXR)

load("2020/data/input.RData")
```

```{r}
st1 = U1
st1[which(st1 > 10)] = 10
tibble(st1) %>%
  count(st1) %>%
  ggplot(aes(x = st1, y = n)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme_bw() +
  xlab("Stoppage time for the first half") +
  ylab("n") +
  scale_x_continuous(breaks = 0:10,
                     labels = c(0:9, "10+"))
```

```{r}
st2 = U2
st2[which(st2 > 10)] = 10
tibble(st2) %>%
  count(st2) %>%
  ggplot(aes(x = st2, y = n)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme_bw() +
  xlab("Stoppage time for the second half") +
  ylab("n") +
  scale_x_continuous(breaks = 0:10,
                     labels = c(0:9, "10+"))
```

The stoppage time for the first half, $U_1$, and the second half, $U_2$, are modeled as:
$$ U_1 \sim \text{Poisson} (\pi_1) $$
$$ U_2 \sim \text{Poisson} (\pi_2) $$
\begin{itemize}
\item $g_t$ is the amount of goals scored in half $t$ until minute 45;
\item $r_t$ is the amount of red cards received in half $t$ until minute 45;
\item $c = \begin{cases}
 1, \text{ if $|x - y| \leq 1$ at minute 45 of the second half;}  \\
 0, \text{ otherwise.}
\end{cases}$
\end{itemize}

```{r}
aic <- function(loglik, k) {
  2*k - 2*loglik
}

bic <- function(loglik, k, n) {
  k*log(n) - 2*loglik
}
```

## Model 1

$$ \pi_1 = \eta_1 $$
$$ \pi_2 = \eta_2 $$

```{r}
eta = Variable(2)
pi1 = eta[1] * rep(1, N)
pi2 = eta[2] * rep(1, N) 
log_lik_st = t(U1) %*% log(pi1) + t(U2) %*% log(pi2) - sum_entries(pi1) - sum_entries(pi2)  
objective = Maximize(log_lik_st)
problem = Problem(objective)
solution = solve(problem, solver = "MOSEK")
mod_1 = list(eta = as.vector(solution$getValue(eta)),
             loglik = solution$value - sum(log(factorial(U1))) - sum(log(factorial(U2))))
mod_1$aic = aic(mod_1$loglik, 2)
mod_1$bic = bic(mod_1$loglik, 2, N)
mod_1
```

\clearpage

## Model 2

$$ \pi_1 = \eta_1 + \phi g_1 $$
$$ \pi_2 = \eta_2 + \phi g_2$$
```{r}
eta = Variable(2)
phi = Variable(1)
pi1 = eta[1] + phi * g1 
pi2 = eta[2] + phi * g2 
log_lik_st = t(U1) %*% log(pi1) + t(U2) %*% log(pi2) - sum_entries(pi1) - sum_entries(pi2)  
objective = Maximize(log_lik_st)
problem = Problem(objective)
solution = solve(problem, solver = "MOSEK")
mod_2 = list(eta = as.vector(solution$getValue(eta)),
             phi = as.vector(solution$getValue(phi)),
             loglik = solution$value - sum(log(factorial(U1))) - sum(log(factorial(U2))))
mod_2$aic = aic(mod_2$loglik, 3)
mod_2$bic = bic(mod_2$loglik, 3, N)
mod_2
```

\clearpage

## Model 3

$$ \pi_1 = \eta_1 + \phi_1 g_1 $$
$$ \pi_2 = \eta_2 + \phi_2 g_2 $$

```{r}
eta = Variable(2)
phi = Variable(2)
pi1 = eta[1] + phi[1] * g1 
pi2 = eta[2] + phi[2] * g2 
log_lik_st = t(U1) %*% log(pi1) + t(U2) %*% log(pi2) - sum_entries(pi1) - sum_entries(pi2)  
objective = Maximize(log_lik_st)
problem = Problem(objective)
solution = solve(problem, solver = "MOSEK")
mod_3 = list(eta = as.vector(solution$getValue(eta)),
             phi = as.vector(solution$getValue(phi)),
             loglik = solution$value - sum(log(factorial(U1))) - sum(log(factorial(U2))))
mod_3$aic = aic(mod_3$loglik, 4)
mod_3$bic = bic(mod_3$loglik, 4, N)
mod_3
```
\clearpage

## Model 4

$$ \pi_1 = \eta_1 + \rho r_1 $$
$$ \pi_2 = \eta_2 + \rho r_2 $$

```{r}
eta = Variable(2)
rho = Variable(1)
pi1 = eta[1] + rho * r1 
pi2 = eta[2] + rho * r2 
log_lik_st = t(U1) %*% log(pi1) + t(U2) %*% log(pi2) - sum_entries(pi1) - sum_entries(pi2)  
objective = Maximize(log_lik_st)
problem = Problem(objective)
solution = solve(problem, solver = "MOSEK")
mod_4 = list(eta = as.vector(solution$getValue(eta)),
             rho = as.vector(solution$getValue(rho)),
             loglik = solution$value - sum(log(factorial(U1))) - sum(log(factorial(U2))))
mod_4$aic = aic(mod_4$loglik, 3)
mod_4$bic = bic(mod_4$loglik, 3, N)
mod_4
```

\clearpage

## Model 5

$$ \pi_1 = \eta_1 + \rho_1 r_1 $$
$$ \pi_2 = \eta_2 + \rho_2 r_2 $$

```{r}
eta = Variable(2)
rho = Variable(2)
pi1 = eta[1] + rho[1] * r1 
pi2 = eta[2] + rho[2] * r2 
log_lik_st = t(U1) %*% log(pi1) + t(U2) %*% log(pi2) - sum_entries(pi1) - sum_entries(pi2)  
objective = Maximize(log_lik_st)
problem = Problem(objective)
solution = solve(problem, solver = "MOSEK")
mod_5 = list(eta = as.vector(solution$getValue(eta)),
             rho = as.vector(solution$getValue(rho)),
             loglik = solution$value - sum(log(factorial(U1))) - sum(log(factorial(U2))))
mod_5$aic = aic(mod_5$loglik, 4)
mod_5$bic = bic(mod_5$loglik, 4, N)
mod_5
```

\clearpage

## Model 6

$$ \pi_1 = \eta_1 + \rho_1 r_1 $$
$$ \pi_2 = \eta_2 + \rho_2 r_2 + \kappa c $$

```{r}
eta = Variable(2)
rho = Variable(2)
kappa = Variable(1)
pi1 = eta[1] + rho[1] * r1 
pi2 = eta[2] + rho[2] * r2 + kappa * c
log_lik_st = t(U1) %*% log(pi1) + t(U2) %*% log(pi2) - sum_entries(pi1) - sum_entries(pi2)  
objective = Maximize(log_lik_st)
problem = Problem(objective)
solution = solve(problem, solver = "MOSEK")
mod_6 = list(eta = as.vector(solution$getValue(eta)),
             rho = as.vector(solution$getValue(rho)),
             kappa = as.vector(solution$getValue(kappa)),
             loglik = solution$value - sum(log(factorial(U1))) - sum(log(factorial(U2))))
mod_6$aic = aic(mod_6$loglik, 5)
mod_6$bic = bic(mod_6$loglik, 5, N)
mod_6
```
\clearpage

```{r}
sum(g1)
```

```{r}
sum(g2)
```

```{r}
sum(r1)
```

```{r}
sum(r2)
```

```{r}
sum(c)
```

