---
title: "Parameters Série A 2019"
output: pdf_document
---

# Rates for the home and away teams

## Model 0
$$\lambda_k = \alpha_i \beta_j \gamma_h$$
$$\mu_k = \alpha_j \beta_i$$

\begin{itemize}
\item $i$: home team index;
\item $j$: away team index;
\item $\alpha$: attack strength parameter;
\item $1/\beta$: defense strength parameter;
\item $\gamma_h$: home advantage parameter.
\end{itemize}

## Model 1
$$\lambda_k(t) = \alpha_i \beta_j \gamma_h$$
$$\mu_k(t) = \alpha_j \beta_i$$

## Model 2
$$\lambda_k(t) = \alpha_i \beta_j \gamma_h \tau^{\mathbb{I}\{\text{half = 2}\}}$$
$$\mu_k(t) = \alpha_j \beta_i \tau^{\mathbb{I}\{\text{half = 2}\}}$$
\begin{itemize}
\item $\tau$: second half parameter.
\end{itemize}

## Model 3
$$\lambda_k(t) = \alpha_i \beta_j \gamma_h \tau^{\mathbb{I}\{\text{half = 2}\}} \lambda_{xy}$$
$$\mu_k(t) = \alpha_j \beta_i \tau^{\mathbb{I}\{\text{half = 2}\}} \mu_{xy}$$
\begin{itemize}
\item $\lambda_{xy} = \begin{cases}
 1, \text{ if $x = y$;}  \\
 \lambda_{10}, \text{ if $x > y$;} \\
 \lambda_{01}, \text{ if $x < y$;}
\end{cases}$

\item $\mu_{xy} = \begin{cases}
 1, \text{ if $x = y$;}  \\
 \mu_{10}, \text{ if $x > y$;} \\
 \mu_{01}, \text{ if $x < y$.}
\end{cases}$
\end{itemize}

# Stoppage time

For all models except model 0, the stoppage time for the first half, $U^1$, and the second half, $U^2$, are modeled as:
$$ U^1 \sim \text{Poisson} (\eta_1 + \phi_1 g^1  )$$
$$ U^2 \sim \text{Poisson} (\eta_2 + \phi_2 g^2 + \kappa c)$$

\begin{itemize}
\item $g^t$ is the amount of goals scored in half $t$ until minute 45;

\item $c = \begin{cases}
 1, \text{ if $|x - y| \leq 1$ at minute 45 of the second half;}  \\
 0, \text{ otherwise.}
\end{cases}$
\end{itemize}

```{r, warning = FALSE, message = FALSE}
# options(OutDec = ",")
options(knitr.kable.NA = "-")

library(dplyr)
library(knitr)

load("dados_serie_a_2019.RData")
load("mod_0.RData")
load("mod_1.RData")
load("mod_2.RData")
load("mod_3.RData")
```

```{r}
alphas = tibble(Time = times$Time,
                mod_0 = exp(mod_0$alpha),
                mod_1 = exp(mod_1$alpha),
                mod_2 = exp(mod_2$alpha),
                mod_3 = exp(mod_3$alpha))
kable(alphas, digits = 4, caption = "Alphas")
```
```{r}
betas = tibble(Time = times$Time,
                mod_0 = exp(mod_0$beta),
                mod_1 = exp(mod_1$beta),
                mod_2 = exp(mod_2$beta),
                mod_3 = exp(mod_3$beta))
kable(betas, digits = 4, caption = "Betas")
```

```{r}
param = tibble(Model = 0:3,
               gamma = c(exp(mod_0$gamma), exp(mod_1$gamma), exp(mod_2$gamma), exp(mod_3$gamma)),
               tau = c(NA, NA, exp(mod_2$tau), exp(mod_3$tau)),
               lambda_10 = c(NA, NA, NA, exp(mod_3$lambda_xy["10"])),
               lambda_01 = c(NA, NA, NA, exp(mod_3$lambda_xy["01"])),
               mu_10 = c(NA, NA, NA, exp(mod_3$mu_xy["10"])),
               mu_01 = c(NA, NA, NA, exp(mod_3$mu_xy["01"])),
               eta_1 = c(NA, mod_1$eta[1], mod_2$eta[1], mod_3$eta[1]),
               eta_2 = c(NA, mod_1$eta[2], mod_2$eta[2], mod_3$eta[2]),
               phi_1 = c(NA, mod_1$phi[1], mod_2$phi[1], mod_3$phi[1]),
               phi_2 = c(NA, mod_1$phi[2], mod_2$phi[2], mod_3$phi[2]),
               kappa = c(NA, mod_1$kappa, mod_2$kappa, mod_3$kappa))
kable(param, digits = 4, caption = "Other parameters",
      col.names = c("Model", "$\\gamma_h$", "$\\tau$", "$\\lambda_{10}$",
                    "$\\lambda_{01}$", "$\\mu_{10}$", "$\\lambda_{01}$", "$\\eta_1$",
                    "$\\eta_2$", "$\\phi_1$", "$\\phi_2$", "$\\kappa$"))
```

