---
title: "Parameters Série A 2020 model r1"
output: pdf_document
---

# Rates for the home and away goals

$$\lambda_k(t) = \alpha_i \beta_j \gamma_h \tau^{\mathbb{I}\{\text{half = 2}\}} e^{x(t)\omega_{\lambda x}} e^{y(t) \omega_{\lambda y}} e^{x^*(t)\omega_{\lambda x^*}} e^{y^*(t) \omega_{\lambda y^*}}$$
$$\mu_k(t) = \alpha_j \beta_i \tau^{\mathbb{I}\{\text{half = 2}\}} e^{x(t)\omega_{\mu x}} e^{y(t) \omega_{\mu y}} e^{x^*(t)\omega_{\mu x^*}} e^{y^*(t) \omega_{\mu y^*}}$$
\begin{itemize}
\item $i$: home team index;
\item $j$: away team index;
\item $\alpha$: attack strength parameter;
\item $1/\beta$: defense strength parameter;
\item $\gamma_h$: home advantage parameter;
\item $\tau$: second half parameter;
\item $x(t)$: the number of goals of the home team until minute t;
\item $y(t)$: the number of goals of the away team until minute t;
\item $x^*(t)$: the number of red cards of the home team until minute t;
\item $y^*(t)$: the number of red cards of the away team until minute t;
\item $\omega_{\lambda x}$, $\omega_{\lambda y}$, $\omega_{\mu x}$ and $\omega_{\mu y}$: parameters that measure the impact of the scored goals in the rates;
\item $\omega_{\lambda x^*}$, $\omega_{\lambda y^*}$, $\omega_{\mu x^*}$ and $\omega_{\mu y^*}$: parameters that measure the impact of the received red cards in the rates.
\end{itemize}

# Rates for the home and away red cards

$$ \lambda_k^*(t) = A_\lambda  \log(t+1 + 45^{\mathbb{I}\{\text{half = 2}\}})$$
$$ \mu_k^*(t) = A_\mu  \log(t+1 + 45^{\mathbb{I}\{\text{half = 2}\}})$$

# Stoppage time

The stoppage time for the first half, $U^1$, and the second half, $U^2$, are modeled as:
$$ U^1 \sim \text{Poisson} (\eta_1 + \phi_1 g^1 + \rho_1 r^1 )$$
$$ U^2 \sim \text{Poisson} (\eta_2 + \phi_2 g^2 + \rho_2 r^2 + \kappa c)$$
\begin{itemize}
\item $g^t$ is the amount of goals scored in half $t$ until minute 45;
\item $r^t$ is the amount of red cards received in half $t$ until minute 45;
\item $c = \begin{cases}
 1, \text{ if $|x - y| \leq 1$ at minute 45 of the second half;}  \\
 0, \text{ otherwise.}
\end{cases}$
\end{itemize}

# Constraint
The constraint for identificability is
$$ \sum_i^n \log(\alpha_i) = \sum_i^n \log(\beta_i).$$
```{r, warning = FALSE, message = FALSE}
options(knitr.kable.NA = "–")

library(dplyr)
library(knitr)

load("data/input.RData")
load("data/mod_r1.RData")
```

```{r}
alphas_betas = tibble(Team = times$Time,
                alpha = exp(mod_r1$alpha),
                beta = exp(mod_r1$beta))
kable(alphas_betas, digits = 4, caption = "Alphas and betas", 
      col.names = c("Team", "$\\alpha$", "$\\beta$"))
```
```{r}
Parameter = c("$\\gamma_h$", "$\\tau$", "$\\omega_{\\lambda x}$",
              "$\\omega_{\\lambda y}$", "$\\omega_{\\mu x}$",
              "$\\omega_{\\mu y}$", "$\\omega_{\\lambda x^*}$",
              "$\\omega_{\\lambda y^*}$", "$\\omega_{\\mu x^*}$",
              "$\\omega_{\\mu y^*}$")
goals = tibble(Parameter, 
               Estimative = c(exp(mod_r1$gamma), exp(mod_r1$tau), mod_r1$omega))
kable(goals, digits = 4, caption = "Goal rate parameters")
```

```{r}
Parameter = c("$A_\\lambda$", "$A_\\mu$")
reds = tibble(Parameter, Estimative = exp(c(mod_r1$a)))
kable(reds, digits = 8, caption = "Red card rate parameters")
```

```{r}
Parameter = c("$\\eta_1$", "$\\eta_2$", "$\\phi_1$", "$\\phi_2$", 
               "$\\rho_1$", "$\\rho_2$", "$\\kappa$")
st = tibble(Parameter, 
            Estimative = c(mod_r1$eta, mod_r1$phi, mod_r1$rho, mod_r1$kappa))
kable(st, digits = 4, caption = "Stoppage time parameters")
```

```{r}
mod_r1$loglik
```

